### 2011-01-22 paper/results.tex
first draft of the results section

\edit{write this.}

@@

\begin{table}
\begin{center}
\begin{tabular}{|r|c|c|c||c|}
\hline
                                         & A       & B      & C      &  Average \\
\hline                                                               
\hline                                                               
Previous hand-coded gait                 & --      & --     & --     &  5.16 \\
\hline                                                                 
Random search                            & 6.04    & 17.26  & 4.90   &  9.40 \\
\hline                                                                 
Uniform Random Hill Climbing             & 11.37   & 9.44   & 2.69   &  7.83 \\
\hline                                                                 
Gaussian Random Hill Climbing            & 3.10    & 13.59  & 13.40  &  10.03 \\
\hline                                                                 
Policy Gradient Descent                  & 0.68    & 14.69  & 3.60   &  6.32 \\
\hline                                                                 
Nelder-Mead simplex                      & 8.51    & 13.62  & 14.83  &  12.32 \\
\hline                                                                 
Linear Regression                        & 27.58   & 12.51  & 1.95   &  14.01 \\
%\hline                                                                
%SVM Regression                           & ???     & ???    & ???   &   \\
%\hline                                                                
%Evolutionary Neural Network (HyperNEAT)  & ???     & ???    & ???   &   \\
\hline
\end{tabular}
\caption{The best gaits found for each starting vector and algorithm,
  in body lengths per minute.}
\tablabel{results_table}
\end{center}
\end{table}

>>>>

\edit{proofread this.}
\subsection{Maximizing Strategies}
The maximizing strategies implemented include uniform random hill climbing, Gaussian random hill climbing, policy gradient descent, and Nelder-Mead simplex. As a group, these strategies produced results similar to gaits randomly generated using the SineModel5 model. None of these strategies consistently outperformed the others in the three trials; A different strategy generated the best gait in each trial. Uniform random hill climbing produced the best gait (11.37 body lengths/minute) in the first trial, with the next best performing strategy (Nelder-Mead simplex) resulting in a gait of 8.51 body lengths/minute. The best gait in the second trial was actually generated randomly (17.26 body-lengths/minute). Gaussian random hill climbing, policy gradient descent, and Nelder-Mead simplex all produced similar best gaits in the second trial, each around 14 body lengths/minute. In the third trial, Nelder-Mead simplex and Gaussian random hill climbing significantly outperformed the other maximizing strategies, resulting in gaits of 14.83 and 13.40 body lengths/minute respectively. Overall, Nelder-Mead simplex performed the best, producing an average best gait of 12.32 body lengths/minute. Gaussian random hill climbing followed, with an average best gait of 10.03 body lengths/minute.

\subsection{Predictive Strategies}
The predictive strategies used were linear regression and support vector regression. In the first trial, linear regression produced a gait (27.58 body lengths/minute) that was over three times faster than the best gait produced by a maximizing strategy (uniform random hill climbing -- 11.37 body lengths/minute). The average of the best gait for the three trials of linear regression was 14.01 body lengths/minute, which was better than the average best gait for the best performing maximizing strategy (Nelder-Mead simplex -- 12.32 body lengths/minute).

As mentioned above, the SVM strategy involved many tunable parameters. The version of SVM tuned for simulation did not show competitive performance on the real robot. We tried tuning some parameters on the real robot, but after some amount of tuning, the method still exhibited too little exploration and easily became stuck in local minima.

\subsection{Evolved Neural Network Strategy}
The evolved neural network strategy used was HyperNEAT. HyperNEAT produced the fastest gaits by far. Linear regression produced a gait in the first trial (27.58 body lengths/minute) that was on par with the best gaits generated by HyperNEAT, by no other maximizing or predictive strategy produced gaits close to those of HyperNEAT. Linear regression was the best performing maximizing or predictive strategy, but it resulted in an average best gait of only 14.01 body lengths/minute. HyperNEAT, on the other hand, resulted in an average best gait of 29.26 body lengths/minute. One issue encountered with HyperNEAT was that it generated gaits that were rougher on the robot than gaits generated by the other strategies. The gaits sometimes caused the motor servos to overheat, which causes the motor to behave differently than expected. Since an overheated motor produces a different walk that expected, a test was performed after each run to make sure all motors were working correctly. If a motor was not, the distance walked would be halved to penalize walks that were harmful to the robot.

\begin{table}
\begin{center}
\begin{tabular}{|r|c|c|c||c|}
\hline
                                         & A       & B      & C      &  Average \\
\hline                                                               
\hline                                                               
Previous hand-coded gait                 & --      & --     & --     &  5.16 \\
\hline                                                                 
Random search                            & 6.04    & 17.26  & 4.90   &  9.40 \\
\hline                                                                 
Uniform Random Hill Climbing             & 11.37   & 9.44   & 2.69   &  7.83 \\
\hline                                                                 
Gaussian Random Hill Climbing            & 3.10    & 13.59  & 13.40  &  10.03 \\
\hline                                                                 
Policy Gradient Descent                  & 0.68    & 14.69  & 3.60   &  6.32 \\
\hline                                                                 
Nelder-Mead simplex                      & 8.51    & 13.62  & 14.83  &  12.32 \\
\hline                                                                 
Linear Regression                        & 27.58   & 12.51  & 1.95   &  14.01 \\
\hline                                                                
Evolutionary Neural Network (HyperNEAT)  & 24.27     & 36.44    & 27.07   & 29.26  \\
\hline
\end{tabular}
\caption{The best gaits found for each starting vector and algorithm,
  in body lengths per minute.}
\tablabel{results_table}
\end{center}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|r|c|c|c||c|}
\hline
                                         & A       & B      & C      &  Average \\
\hline                                                               
\hline                                                               
Previous hand-coded gait                 & --      & --     & --     &  5.16 \\
\hline                                                                 
Random search                            & 6.04    & 17.26  & 4.90   &  9.40 \\
\hline                                                                 
Uniform Random Hill Climbing             & 11.37   & 9.44   & 2.69   &  7.83 \\
\hline                                                                 
Gaussian Random Hill Climbing            & 3.10    & 13.59  & 13.40  &  10.03 \\
\hline                                                                 
Policy Gradient Descent                  & 0.68    & 14.69  & 3.60   &  6.32 \\
\hline                                                                 
Nelder-Mead simplex                      & 8.51    & 13.62  & 14.83  &  12.32 \\
\hline                                                                 
Linear Regression                        & 27.58   & 12.51  & 1.95   &  14.01 \\
\hline                                                                
Evolutionary Neural Network (HyperNEAT)  & 24.27     & 36.44    & 27.07   & 29.26  \\
\hline
\end{tabular}
\caption{The best gaits found for each starting vector and algorithm,
  in body lengths per minute.}
\tablabel{results_table}
\end{center}
\end{table}
